Analysis Output files

### 2021-10-07 code/data-analysis/config-file-generator.Rmd
Revision

```{r List of Sources}
so <- c("Yr_Biomass","Yr_Coal","Yr_Metal","Yr_Oil",
         "Yr_Salt","Yr_Soil","Yr_Steel","Yr_Traffic")
```

@@

>>>>

```{r List of Sources}
so <- c("Yr_Biomass","Yr_Coal","Yr_Metals","Yr_Oil",
         "Yr_Salt","Yr_Soil","Yr_Steel","Yr_Traffic")
```

@@

```{r ses adj. model for apportioned mass factor}
dataname <- "ndi-mass-fac.csv"
expo <- so

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz.sub),1)){
      w <- gsub("outcome", cuz.sub[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz.sub)*(i-1)
      writeLines(w, here('config-files','mass-fac-ses', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

### 2021-10-07 code/data-analysis/output-cleaning.Rmd
Revision

```{r Load data}
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ec-1yr.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
load(here('data','processed','pmc-sub-5yr.RDa'))
load(here('data','processed','mass-app-1yr-c2.RDa'))
load(here('data','processed','site-urban-ses-cat.RDa'))
```

@@

@@

```{r Output Factors Ex. EC Base}
out.fac.base <- read.csv(here('output','analysis','fac-base.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.1yr.iqr) %>% 
  merge(Factor.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

@@

```{r Output Factors Ex. EC SES-Adj}
out.fac.ses <- read.csv(here('output','analysis','fac-ses.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.1yr.iqr) %>% 
  merge(Factor.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

@@

```{r Output Factors Base}
out.fac.ec.base <- read.csv(here('output','analysis','fac-ec-base.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.ec.1yr.iqr) %>% 
  merge(Factor.ec.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

@@

```{r Output Factors SES-Adj}
out.fac.ec.ses <- read.csv(here('output','analysis','fac-ec-ses.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.ec.1yr.iqr) %>% 
  merge(Factor.ec.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

@@

@@

```{r Output Factor Region}
out.fac.region = data.frame()
for (i in c("west", "midwest", "south", "northeast")){
  dt <- read.csv(here('output','analysis',paste('fac-',i,'.csv', sep= ""))) %>% 
    mutate(Region = i)
  out.fac.region  <-  rbind(out.fac.region, dt)
}

out.fac.region <- out.fac.region %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.1yr.iqr) %>% 
  merge(Factor.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, Region, HR, HR.L, HR.U)

>>>>

```{r Load data}
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ec-1yr.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
load(here('data','processed','pmc-sub-5yr.RDa'))
#load(here('data','processed','mass-app-1yr-c2.RDa'))
load(here('data','processed','mass-app-1yr-fac.RDa'))
load(here('data','processed','site-urban-ses-cat.RDa'))
```

@@

### Source Apportioned PM Mass with Factors
mass.fac.1yr.iqr <- dt.mass.app.1yr.fac %>% 
  summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
  pivot_longer(cols = Biomass:Traffic,
               names_to = "Parameter",
               values_to = "IQR")%>% 
  mutate(Parameter = as.factor(Parameter))

@@

```{r Output Factors Base}
out.fac.base <- read.csv(here('output','analysis','fac-base.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.1yr.iqr) %>% 
  merge(Factor.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

@@

```{r Output Factors SES-Adj}
out.fac.ses <- read.csv(here('output','analysis','fac-ses.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.1yr.iqr) %>% 
  merge(Factor.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

@@

```{r Output Factors Inc. EC Base}
out.fac.ec.base <- read.csv(here('output','analysis','fac-ec-base.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.ec.1yr.iqr) %>% 
  merge(Factor.ec.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

@@

```{r Output Factors Factors Inc. EC SES-Adj}
out.fac.ec.ses <- read.csv(here('output','analysis','fac-ec-ses.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.ec.1yr.iqr) %>% 
  merge(Factor.ec.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

@@

```{r Output App Mass Factor SES-Adj}
out.mass.fac.ses <- read.csv(here('output','analysis','mass-fac-ses.csv')) %>%
  mutate(Parameter = gsub(".*Yr_", "", Predictor),
         Parameter = as.factor(Parameter)) %>%  
  merge(mass.fac.1yr.iqr) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3),
         Index = Parameter) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

save(out.mass.fac.ses, file = here('output','analysis','out-mass-fac-ses.RDa'))
```

@@

```{r Output Factor Region}
out.fac.region.2 = data.frame()
for (i in c("west", "midwest", "south", "northeast")){
  dt <- read.csv(here('output','analysis',paste('fac-',i,'.csv', sep= ""))) %>% 
    mutate(Region = i)
  out.fac.region.2  <-  rbind(out.fac.region.2, dt)
}

out.fac.region.2 <- out.fac.region.2 %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.1yr.iqr) %>% 
  merge(Factor.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, Region, HR, HR.L, HR.U)
